---
title: "RepData_PeerAssessment1"
author: "Cyrus Safaie"
date: "August 7, 2016"
output: github_document 
---
1. Code for reading in the dataset and/or processing the data

```{r}
library(knitr)
library(rmarkdown)
```


```{r}


activity=read.csv("activity.csv")
activity2=subset(activity,activity$steps!="NA")
head(activity)
```


2. Histogram of the total number of steps taken each day

```{r}
ag.data=aggregate(activity2$steps, by=list(activity2$date), FUN=sum)
dev.off()
hist(ag.data$x)
library(ggplot2)
#qplot(ag.data$x)+stat_bin(bins=5)
```



3. Mean and median number of steps taken each day
```{r}

c(mean(ag.data$x),median(ag.data$x))

ag.mean=aggregate(activity2$steps, by=list(activity2$date), FUN=mean)
ag.median=aggregate(activity2$steps, by=list(activity2$date), FUN=median)

```


4. Time series plot of the average number of steps takent

```{r}
plot(ag.mean$x,type = "l")
```

5. The 5-minute interval that, on average, contains the maximum number of steps

```{r}
interval.mean=aggregate(activity2$steps, by=list(activity2$interval), FUN=mean)
which.max(interval.mean$x)
max(interval.mean$x)

```


6. Code to describe and show a strategy for imputing missing data
```{r}
# replacing na with 0
activity[is.na(activity)]=0

```

7. Histogram of the total number of steps taken each day after missing values are imputed

```{r}
hist(aggregate(activity$steps, by=list(activity$date), FUN=sum)[,2])

```


8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}

activity$wkDY=rep("weekday",length(activity$date))

activity$wkDY[(weekdays(as.Date(activity$date))=="Sunday") | (weekdays(as.Date(activity$date))=="Saturday")]="weekend"


par(mfrow = c(2, 1))
for (type in c("weekend", "weekday")) {
        steps.type <- aggregate(steps ~ interval, data = activity, subset = activity$wkDY == 
                                        type, FUN = mean)
        plot(steps.type, type = "l", main = type)
}

```
